Longitudinal Manifold Estimation

### 2023-02-24 paper/main.tex
fix compilation errors

\usepackage[english]{babel}

@@

\For{t = 1, 2, \dots, T} {
  Apply modified PME algorithm with $\pi_{f_t(0)}(\mu_{j, N_t, t}) \gets \left\{r_{j, t}\right\}_{j = 1}^N_t$ and obtain $f_t^*$ and $\lambda_t^*$\;
  $\left\{r_{j, t}\right\} \gets \pi_{f_t^*}(\mu_{j, N_t, t})$ for $j = 1, \dots, N_t$ and $x_{j, t} \gets f_t^*(r_{j, t})$ for $j = 1, \dots, N_t$\;
  Add column vector $\mathbf{t}$ as first column of $\mathbf{r}$\;
}

@@

\nocite{*}
\bibliographystyle{plain}
%\bibliography{references}
\printbibliography

>>>>

\usepackage{csquotes}
\usepackage[english]{babel}

@@

\For{t = 1, 2, \dots, T} {
  Apply modified PME algorithm with $\pi_{f_t(0)}(\mu_{j, N_t, t}) \gets \left\{r_{j, t}\right\}_{j = 1}^{N_t}$ and obtain $f_t^*$ and $\lambda_t^*$\;
  $\left\{r_{j, t}\right\} \gets \pi_{f_t^*}(\mu_{j, N_t, t})$ for $j = 1, \dots, N_t$ and $x_{j, t} \gets f_t^*(r_{j, t})$ for $j = 1, \dots, N_t$\;
  Add column vector $\mathbf{t}$ as first column of $\mathbf{r}$\;
}

@@

\nocite{*}
%\bibliographystyle{plain}
%\bibliography{references}
\printbibliography
